\documentclass{article}

\usepackage{hyperref}

\title{ECE-210-A Syllabus}
\author{Instructor: Jonathan Lam}
\date{Spring 2022}

\begin{document}
\maketitle
\noindent\textbf{Meeting Time}: Wednesdays, 4-5PM \\
\textbf{Venue}: MS Teams (online), NAB 803 (in person) \\
\textbf{Contact}: \href{mailto:lam12@cooper.edu}{lam12@cooper.edu} or Teams chat

\subsection*{Course Overview}
The course material for ECE-210 is a general survey of MATLAB as a scientific programming language, specifically tailored but not limited to its applications in the realm of signals processing. Signals and Systems is a corequisite in the sense that the material from ECE-210 is necessary to perform well in that course, but not the other way around.

There will also be review sessions for the ECE-211 sessions. A recorded walkthrough of a previous year's exam will be provided, and during our meeting time we will field questions or go through problems in more detail.

This course is 0 credits and your final grade will be Pass or Fail. Nine homeworks will be assigned nearly one each week of the semester. Homeworks are to be submitted by email on Teams by their marked deadlines (usually 11:59PM the Wednesday after they are assigned).

\subsection*{Grading}
Each homework assignment will be graded on a scale from 0-3 points dependent on timeliness, completeness, correctness (2 points) and style (1 point). Homeworks may be resubmitted within one week of being returned for full credit. To pass ECE-210, you need only to earn 18 points from the nine homeworks for the semester. Grades on homeworks will be returned within two weeks of submission via Teams.

Attendance is mandatory and will be taken. If you cannot make it to class for some reason or another (e.g., quarantining), please let Prof. Fontaine or me know. All lectures will be screen-recorded in case students cannot attend, but this is not a reason for unexcused absences.

Cheating in this course will not be tolerated; any blatant cheating will earn you two zero homework grades, and suspected cheating could earn the class pop quizzes. For everyone's sake, don't! You are better off asking lots of questions or handing in an assignment late than blindly copying from your classmate.

\clearpage
\subsection*{Contact}
Any questions regarding the homeworks or lecture may be emailed to me at any time. Questions regarding Signals and Systems may be directed towards myself as well, although they are often better left for Professor Fontaine.

All course materials, including homeworks, lessons and will be uploaded to the Teams channel shortly after the associated lecture. This syllabus is subject to change, but I will try to update the version on Teams and give ample verbal notification of any policy changes should change happen.
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
