\documentclass[11pt]{article}
\usepackage{geometry}
\title{ECE-210-B Syllabus}
\author{Samuel Maltz}
\date{Spring 2020}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{Samuel Maltz}
\lhead{ECE-210B Syllabus}
\rfoot{\thepage}

\renewcommand{\headrulewidth}{0pt}

\begin{document}
\noindent\textbf{Meeting Time}: Wednesdays, 5PM - 6PM \\
\textbf{Room}: 806 \\
\textbf{Email}: \textit{maltz@cooper.edu} \\ \\
\textbf{Course Overview}: The course material for ECE-210 is a general survey of MATLAB as a programming language, specifically tailored but not limited to its applications in the realm of signals processing. ECE-211: Signals and Systems is a corequisite in the sense that the material from ECE-210 is necessary to perform well in that course, but no substantial knowledge from Signals and Systems is expected of students in ECE-210. \\
This course is 0 credits and your final grade will be Pass or Fail. Nine homeworks will be assigned nearly one each week of the semester. Homeworks are to be submitted by email to \textit{maltz@cooper.edu} as \textit{.m} files by 11:59 PM the Wednesday after they are assigned unless otherwise stated. \\ \\
\textbf{Grading}: Each homework assignment will be graded as a Pass or Fail dependent on timeliness, completeness, correctness and style. Homeworks that receive a failing grade for style may be resubmitted within a week with no penalty, while homeworks that receive a failing grade for any other reason may be resubmitted within a week for half credit. To pass ECE-210, you need only to earn a passing grade on seven of the nine homeworks for the semester. Grades on homeworks will be returned within two weeks of submission via email.\\
Attendance is mandatory, and an unexcused absence means that you may receive no more than half credit for your next homework assignment. If you must be absent for any reason, please email me before lecture begins. Homeworks are different between sections and students registered for ECE-210B must submit the homework for ECE-210B.\\ 
Cheating in this course in the form of blindly copying lines of code from your classmates for homework assignments will not be tolerated; any blatant cheating will earn you two failing homework grades. You are better off asking lots of questions or handing in an assignment late than blindly copying from your classmate. \\ \\
\textbf{Contact}: Any questions regarding the homeworks or lecture may be emailed to me at any time. Face-to-face tutoring may be offered through the Electrical Engineering department, appointments for which can be made by emailing me. Questions regarding Signals and Systems may be directed towards myself and the other ECE-210 instructors as well, although they are often better left for Professor Fontaine. If I do not respond to an email in apt time, chances are that I am \textit{not} ignoring you. Please just email me again! \\
\end{document}