\documentclass{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{hyperref}

\usepackage{minted}

\title{ECE-210-A HW6}
\author{Instructor: Jonathan Lam}
\date{Spring 2022}

\begin{document}

\maketitle

\noindent This homework concerns digital filters and the Z-transform.
\begin{enumerate}
\item For this question, you will work with the discrete-time system described by the following transfer function:
  \begin{equation*}
    H(z)=\frac{\frac{1}{2}+\frac{2}{3}z+\frac{3}{7}z^2}{3+\frac{1}{3}z+\frac{1}{2}z^3}
  \end{equation*}
  \begin{enumerate}
  \item Store the transfer function in coefficient vectors \mintinline{matlab}|b| and \mintinline{matlab}|a| for the numerator and denominator, respectively.

    Be \textbf{very} careful setting this up. See \mintinline{matlab}|help zplane| to see the format that \mintinline{matlab}|zplane| expects the polynomial functions to be in. (Hint: you may need to left-pad one of \mintinline{matlab}|a| or \mintinline{matlab}|b| with zero(s).)

  \item Plot the poles and zeros of this system using a MATLAB function and the transfer function coefficients. List the ROCs (regions of convergence) and state whether each ROC is causal and/or stable.

  \item Compute the poles and zeros of this system using a MATLAB function. Do these poles and zeros match what you saw in the previous question? (\textit{Optional.} Calculate the poles and zeros by hand and verify once again that these are correct.)

  \item Compute the first 32 samples of the impulse response of this transfer function using a MATLAB function and save this to a variable \mintinline{matlab}|h|.

  \item Generate a 64-length vector $x[n]=\left(-\frac{5}{6}\right)^n$, $0\le n<64$. This is an arbitrary discrete-time signal. Show the result of applying the filter with transfer function $H(z)$ to this signal by:
    \begin{enumerate}
    \item Using \mintinline{matlab}|filter|.
    \item Convolution in the time-domain with the impulse response.
    \item \textit{(Optional.)} Multiplication in the z-domain. Show your work.

      (Note that you can use \mintinline{matlab}|impz| to take inverse Z-transform of a rational function.)
    \end{enumerate}
    Truncate the filtered signals to the first 32 samples before plotting them. Do your output signals match? (Note that \mintinline{matlab}|conv| will produce a vector of different length than $x$ -- this is inconsequential and you can truncate it to the correct length.)
  \end{enumerate}

\item We're going to be exploring a filter by placing its poles and zeros in specific locations. Last question you converted a system description from its transfer function (tf form) to its zeros and poles (zp(k) form). Now we will do the opposite.
  \begin{enumerate}
  \item Compute numerator and denominator vectors for a transfer function with $k=0.1$ and these poles and zeros:

    Poles: $0.7375\exp(\pm0.7601j)$, $0.9589\exp(\pm1.2360j)$

    Zeros: $\exp(\pm2.056j)$, $\exp(\pm1.4261j)$

  \item Create a pole-zero plot using the numerator and denominator vectors and a MATLAB function.

  \item Use \mintinline{matlab}|freqz| as shown in lecture to find the frequency response of this filter. This will return two vectors: $H$ (complex frequency response vector) and $\omega$ (digital frequencies corresponding to $H$).

    Do not use the default plot created by \mintinline{matlab}|freqz| -- you will be manually creating the plot. (The default plot is shown if you do not use the return value of \mintinline{matlab}|freqz|, so make sure to save the values \mintinline{matlab}|[H, w]| for the next question.)

  \item $H$ is complex: it has a magnitude and a phase. Plot these in two subplots similar to what was shown in lecture. Make sure to:
    \begin{itemize}
    \item Convert the magnitude gain (magnitude of $H$) in decibels and label accordingly.
    \item Plot the delay (phase of $H$) in degrees. Use \mintinline{matlab}|unwrap| to make it look nicer. (Note that for this particular filter, there are jagged edges even with \mintinline{matlab}|unwrap| because it is a sharp filter. However, without unwrap you get some additional unwanted jagged edges.)
    \item Show units in axis labels. (Remember that the frequency vector $w$ is in digital units of radians, not radians per second.)
    \item Remember that the frequency vector $w$ goes only from $0$ to $\pi$. Properly scale and limit and label the x-axis using \mintinline{matlab}|xlim|, \mintinline{matlab}|xticks|, and \mintinline{matlab}|xticklabels|.
    \end{itemize}

  \item Using the information from the frequency response, what kind of filter is this (high/low/band-pass)? Can you see this from the pole-zero plot as well?

  \item \textit{(Optional.)} Choose a sampling frequency $f_s$ and apply the filter to sinusoids at $f\in\{0.1f_s/2,0.5f_s/2,0.9f_s/2\}$ and see that this indeed attenuates frequencies as you expect.
  \end{enumerate}
\end{enumerate}

\end{document}
