\documentclass[11pt]{article}
\usepackage{geometry}
\title{ECE-210-B Syllabus}
\author{Husam Almanakly}
\date{Spring 2022}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Husam Almanakly}
\lhead{ECE-210B Syllabus}
\rfoot{\thepage}

\renewcommand{\headrulewidth}{0pt}

\begin{document}
\noindent\textbf{Meeting Time}: Wednesdays, 5PM - 6PM \\
\textbf{Meetings}: Microsoft Teams \\
\textbf{Email}: \textit{husam.almanakly@cooper.edu} \\ \\
\textbf{Course Overview}: The course material for ECE-210 is a general survey of MATLAB as a programming language, specifically tailored but not limited to its applications in the realm of signals processing. ECE-211: Signals and Systems is a corequisite in the sense that the material from ECE-210 is necessary to perform well in that course, but no substantial knowledge from Signals and Systems is expected of students in ECE-210. \\

This course is 0 credits and your final grade will be Pass or Fail. Nine homeworks will be assigned nearly one each week of the semester. Homeworks are to be submitted on your respective Teams channel as \textit{.m} files by 11:59 PM the Wednesday after they are assigned unless otherwise stated. \\ \\
\textbf{Grading}: Each homework assignment will be graded as a Pass or Fail depending on completeness, correctness, and style. Homeworks that receive a failing grade for style may be resubmitted within a week with no penalty. To pass ECE-210, you need only to earn a passing grade on seven of the nine homeworks for the semester. Grades on homeworks will be returned within two weeks of submission through your Teams channel.\\

Attendance is mandatory, and an unexcused absence means that you may receive no more than half credit for your next homework assignment. If you must be absent for any reason, please email me or message me on Teams before lecture begins. Homeworks are different between sections and students registered for ECE-210B must submit the homework for ECE-210B.\\ 

Cheating in any form will not be tolerated in this class; any blatant cheating will result in two failing homework assignments for each student. If you need an extension, you're better off sending me a message on Teams than copying someone else's code. \\ \\
\textbf{Contact}: Feel free to reach out to me via email or Teams for any questions on the lectures or the homework assignments. Questions regarding Signals and Systems may be directed towards myself and the other ECE-210 instructors as well, although they are often better left for Professor Fontaine. \\
\end{document}